Calendar-based graphics for visualizing people's daily schedules

### 2018-10-08 preamble.tex
reformatted to R Journal style

\usepackage{monashwp}

% META DATA

\wp{16/99}

\jel{C10,C14,C22}

\addresses{
  \textbf{Earo Wang}\\
      Department of Econometrics and Business Statistics,\\
      Monash University, VIC 3800\\
      Australia.\\
      Email: earo.wang@monash.edu\\[1cm]
  \textbf{Di Cook}\\
      Department of Econometrics and Business Statistics,\\
      Monash University, VIC 3800\\
      Australia.\\
      Email: dicook@monash.edu\\[1cm]
  \textbf{Rob J Hyndman}\\
      Department of Econometrics and Business Statistics,\\
      Monash University, VIC 3800\\
      Australia.\\
      Email: rob.hyndman@monash.edu
}

\lfoot{\sf Wang, Cook \& Hyndman: \Date~\Month~\Year}

>>>>

% Any extra LaTeX you need in the preamble
\usepackage{amsmath}
